Models

### 2021-07-26 analysis/05_model_metrics.Rmd
clean up

#taxa model
taxa_slope <- study_slope_data %>%
  #filter(metric %in%  c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_next")) %>%
  group_nest(metric) %>%
  mutate(#year_center = map(data, ~scale(.x$year)),
         #model = map(data, ~lmer(estimate ~ taxa + (1|taxa), 
         model = map(data, ~glm(estimate ~ taxa, 
                                 data = .x)),
           coef = map(model, tidy),
           ) %>% 
  select(metric, coef) %>%
  unnest(cols = c(coef)) %>%
  mutate(covariate = "taxa")

>>>>

#taxa model
taxa_slope <- study_slope_data %>%
  mutate(taxa = as.factor(taxa)) %>%
  #filter(metric %in%  c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_next")) %>%
  group_nest(metric) %>%
  mutate(model = map(data, ~glm(estimate ~ taxa, 
                                 data = .x)),
           coef = map(model, tidy),
           ) %>% 
  select(metric, coef) %>%
  unnest(cols = c(coef)) %>%
  mutate(covariate = "taxa")
